CL-PFU: A suite of R packages for energy conversion chain analysis

### 2023-08-17 paper.Rmd
Minor changes.

<!-- This paper describes a suite of packages -->
<!-- to assist SEA practitioners to analyze  -->
<!-- energy movement through society.  -->
<!-- The new packages enable analysis of any country in the world -->
<!-- across timespans of decades or longer. -->
<!-- In short, the packages enable, for the first time,  -->
<!-- scalable Societal Exergy Analysis (SEA). -->

@@

<!-- No portion of this paper has been submitted or published -->
<!-- in another peer-reviewed journal.  -->
<!-- A paper with a very different focus  -->
<!-- (efficiency results from the full CL-PFU database) -->
<!-- is in preparation. -->
<!-- Our desire is that the results paper will reference -->
<!-- this JOSS paper. -->

<!-- Define some macros to use later -->
[link-cran]:             https://cran.r-project.org
[link-ecctools]:         https://github.com/earamendia/ECCTools
[link-eroitools]:        https://github.com/earamendia/EROITools
[link-ieatools]:         https://github.com/MatthewHeun/IEATools
[link-ieaweeb]:          https://www.iea.org/data-and-statistics/data-product/world-energy-balances
[link-ilo]:              https://www.ilo.org/
[link-fao]:              https://www.fao.org/
[link-matsbyname]:       https://github.com/MatthewHeun/matsbyname
[link-matsindf]:         https://github.com/MatthewHeun/matsindf
[link-mwtools]:          https://github.com/EnergyEconomyDecoupling/MWTools
[link-pfusetup]:         https://github.com/EnergyEconomyDecoupling/PFUSetup
[link-pfudatabase]:      https://github.com/EnergyEconomyDecoupling/PFUDatabase
[link-pfuaggdatabase]:   https://github.com/EnergyEconomyDecoupling/PFUAggDatabase
[link-pfupipelinetools]: https://github.com/EnergyEconomyDecoupling/PFUPipelineTools
[link-pins]:             https://pins.rstudio.com
[link-rclabels]:         https://github.com/MatthewHeun/RCLabels
[link-recca]:            https://github.com/MatthewHeun/Recca
[link-targets]:          https://docs.ropensci.org/targets
[link-tidyverse]:        https://www.tidyverse.org

>>>>

<!-- This paper describes a suite of packages -->
<!-- to assist Societal Exergy Analysis practitioners to analyze  -->
<!-- energy movement through society.  -->
<!-- The new packages enable analysis of any country in the world -->
<!-- across timespans of decades or longer. -->
<!-- In short, the packages enable, for the first time, scalable SEA. -->

@@

<!-- No portion of this paper has been submitted or published -->
<!-- in another peer-reviewed journal.  -->
<!-- A paper with a very different focus  -->
<!-- (efficiency results from the full CL-PFU database) -->
<!-- is in preparation for the IOP journal -->
<!-- Environmental Research: Energy. -->
<!-- It is our desire that the Environmental Research: Energy -->
<!-- paper will reference this JOSS paper. -->

<!-- ---Matthew Kuperus Heun, 17 August 2023 -->

<!-- Define some macros for later use -->
[link-cran]:             https://cran.r-project.org
[link-ecctools]:         https://github.com/earamendia/ECCTools
[link-eroitools]:        https://github.com/earamendia/EROITools
[link-ieatools]:         https://github.com/MatthewHeun/IEATools
[link-ieaweeb]:          https://www.iea.org/data-and-statistics/data-product/world-energy-balances
[link-ilo]:              https://www.ilo.org/
[link-fao]:              https://www.fao.org/
[link-matsbyname]:       https://github.com/MatthewHeun/matsbyname
[link-matsindf]:         https://github.com/MatthewHeun/matsindf
[link-mwtools]:          https://github.com/EnergyEconomyDecoupling/MWTools
[link-pfusetup]:         https://github.com/EnergyEconomyDecoupling/PFUSetup
[link-pfudatabase]:      https://github.com/EnergyEconomyDecoupling/PFUDatabase
[link-pfuaggdatabase]:   https://github.com/EnergyEconomyDecoupling/PFUAggDatabase
[link-pfupipelinetools]: https://github.com/EnergyEconomyDecoupling/PFUPipelineTools
[link-pins]:             https://pins.rstudio.com
[link-rclabels]:         https://github.com/MatthewHeun/RCLabels
[link-recca]:            https://github.com/MatthewHeun/Recca
[link-targets]:          https://docs.ropensci.org/targets
[link-tidyverse]:        https://www.tidyverse.org
